Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-03 ms.tex
Wrote a bit about case study

% Highlighte inline code
\definecolor{light-gray}{gray}{0.95}
%\newcommand{\code}[1]{\mbox {\texttt{#1}}}
\newcommand{\code}[1]{\colorbox{light-gray}{\color{RawSienna}\texttt{#1}}}

@@

In this paper we will go through a case study, an example simulation, where we
use many of the useful features Atomify provides.
We start by discussing the GUI in section \ref{sec:features} where the main features are summarized.
In section \ref{sec:casestudy}, the case study is introduced where we go through a typical example
of a simulation that uses regions and groups to perform different integration on different atoms.
Details about how Atomify runs LAMMPS is found in section \ref{sec:implementation} where the data flow and the threading model is explained.
Finally, we summarize the work in our paper in section \ref{sec:conclusion} with some thoughts about future outlooks in section \ref{sec:future}.

@@

\section{\label{sec:casestudy}Case study: flow through nanoporous media}
Fluid flow is often characterized with permeability, the inverse flow resistance of a material.
The permeability can be measured using Darcy's law when applying a pressure gradient.

Humans use an enormous amount of energy, most of which comes from chemical reactons in burning hydrocarbons.
\todo{Short motivation about flow in nanoporous media}

>>>>

% Highlighte inline code
\definecolor{light-gray}{gray}{0.95}
\definecolor{atomify-red}{rgb}{0.90196078 , 0.09803922, 0.29411765}
\definecolor{atomify-green}{rgb}{0.23529412 , 0.70588235, 0.29411765}
\definecolor{atomify-yellow}{rgb}{0.8,  0.70588235,  0.07843138}
\definecolor{atomify-blue}{rgb}{0.00000000 , 0.50980392, 0.78431373}
%\newcommand{\code}[1]{\mbox {\texttt{#1}}}
\newcommand{\code}[1]{\colorbox{light-gray}{\color{RawSienna}\texttt{#1}}}

@@

In this paper we will go through a case study, an example simulation, where we
use many of the useful features Atomify provides.
We start by discussing the GUI in section \ref{sec:features} where the main features are summarized.
In section \ref{sec:casestudy}, the case study is introduced where we go through a typical example
of a simulation that uses regions and groups to perform different integration on different atoms.
Common pitfalls which are easily picked up with Atomify are shown.
Details about how Atomify runs LAMMPS is found in section \ref{sec:implementation} where the data flow and the threading model is explained.
Finally, we summarize the work in our paper in section \ref{sec:conclusion} with some thoughts about future outlooks in section \ref{sec:future}.

@@

\section{\label{sec:casestudy}Case study: flow through nanoporous media}
\todo{Short motivation about flow in nanoporous media with references}
Fluid flow is often characterized with permeability, the inverse flow resistance of a material.
The permeability can be measured using Darcy's law when applying a pressure gradient.
However, the derivation of Darcy's law assume no-slip boundary conditions, i.e. the fluid velocity is zero at the boundary of a channel.
This is a good approximation for liquids in large pores, but if the channel diameter $L$ is similar or smaller than the mean free path of the fluid $\lambda$, this is no longer the case.
The Knudsen number, $\text{Kn} = \lambda / L$ quantifies this and can be used with the Klinkenberg correction to correctly describe the effective permeability as a function of pressure in the high Knudsen number limit.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
	\caption{
		Initial configuration in our case study simulation.
		A periodic box consisting of $(40\times20\times20)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder of 5 unit cell radius.
		The different colors indicate the regions of which different integration rules apply.
		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} atoms (gas atoms) have an applied constant acceleration representing the pressure gradient.
		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
    }
	\label{fig:cylinder_simulation}
\end{figure}

In this case study, we will use Atomify to measure the velocity profile of a Lennard Jones gas with varying density to observe the slip velocity effect at low densities.
We will create a nanotube inside a Lennard Jones solid of size  $(40\times20\times20)$ unit cells, reduced density $\rho^* = 0.8442$, where the fluid will flow due to an induced pressure gradient, see figure \ref{fig:cylinder_simulation}.
Here we apply a pressure gradient $\nabla P$ in the $x$-direction on the gas atoms using a constant acceleration $a$
\begin{align}
	a = \frac{\nabla P}{\rho_m},
\end{align}
where $\rho_m$ is the mass density of the gas atoms.
Applying such an acceleration means adding energy to the system which in turn will increase the temperature and eventually melt the system.
We want to couple the solid to an external heat bath so the added energy can be transferred out through a thermostat.
Even though we only apply a pressure gradient on the gas atoms, this induced momentum will also be transferred to the solid atoms which eventually will start moving in the positive $x$-direction which is not desired.
We therefore freeze the outmost atoms.
To achieve these properties of the system, the atoms are divided into multiple regions, which are integrated differently:

\begin{itemize}  
	\item $r \leq 5$: applied pressure gradient
	\item $5 < r \leq 9$: regular time integration
	\item $9 < r \leq 12$: Dissipative Langevin thermostat
	\item $12 < r$: frozen.
\end{itemize}
